Tree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-22 manuscript/climate_sensitivity_draft.Rmd
minor changes

text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) |  currently ~6000 (strict limit 6,500)	 |	No. of figures | 	2 (both colour)
Summary|  	## (limit 200) | 	No. of Tables | 	5  
Introduction|	currently ~1536 |	No of Supporting Information files | 	###.
Materials and Methods |	currently ~1442	||	 
Results |	currently ~1437	 ||
Discussion |	currently ~1339	+ ~200 unwritten (limit 30% of total (not strict), or 1950 if manuscript reaches word limit)	||
Acknowledgements | 	~75 unwritten	||

@@

### Summary (**needs work**)
- Predicting forest responses to drought is an increasingly critical task under climate change effects.
[Part of the problem is due to the lack of studies analyzing the confluence of leaf hydraulic traits with biophysical parameters.]

@@

Although the physiological mechanisms discussed above lead to generally consistent directions of growth responses to tree height and hydaulic traits across droughts, indicating the universality of the underlying mechanisms, the relative importantance of the drivers varied widely across droughts, indicating an interaction with drought characteristics (Tables 4-5). [**DISCUSS DIFFERENCES ACROSS DROUGHTS-- e.g., 1966 was preceded by two dry years, and height mattered most in this drought. ...**] Of course, site characteristics also define the nature of droughts, and comparisons of size and trait effects across sites would be of great value to elucidating the mechanisms through which these shape drought resistance (**check for refs**). Unfortunately, our ability to compare forest responses across droughts is hampered by the fact that droughts are rarely explicitly defined in ecological studies [@slette_how_2019]. Further research will be required to understand how drought characteristics interact with driver variables to shape tree growth responses.

>>>>

text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) |  currently ~6000 (strict limit 6,500)	 |	No. of figures | 	2 (both colour)
Summary|  	## (limit 200) | 	No. of Tables | 	5  
Introduction|	currently ~1536 |	No of Supporting Information files | 	###.
Materials and Methods |	currently ~1442	||	 
Results |	currently ~1437	 ||
Discussion |	currently ~1881 (limit 30% of total (not strict), or 1950 if manuscript reaches word limit)	||
Acknowledgements | 	~75 unwritten	||

@@

### Summary (**needs work**)
- As the climate changes, driving increased drought in many forested regions around the world, mechanistic understanding of factors conferring drought vulnerability and resistance in trees is increasingly important. Yet it remains unclear how tree size and species' traits interactively shape tree growth responses across droughts.

@@

Although the physiological mechanisms discussed above lead to generally consistent directions of growth responses to tree height and hydaulic traits across droughts, indicating the universality of the underlying mechanisms, the relative importantance of the drivers varied widely across droughts, indicating an interaction with drought characteristics (Tables 4-5). [**BRIEFLY DISCUSS DIFFERENCES ACROSS DROUGHTS-- e.g., 1966 was preceded by two dry years, and height mattered most in this drought. ...**] Of course, site characteristics also define the nature of droughts, and comparisons of size and trait effects across sites would be of great value to elucidating the mechanisms through which these shape drought resistance (**check for refs**). Unfortunately, our ability to compare forest responses across droughts is hampered by the fact that droughts are rarely explicitly defined in ecological studies [@slette_how_2019]. Further research will be required to understand how drought characteristics interact with driver variables to shape tree growth responses.
